% resume.tex

% Document settings -----------------------------------------------------------

\documentclass{article}
\usepackage[a4paper, margin=2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{calc}
\usepackage{shading}

\pagestyle{empty}
\raggedbottom
\raggedright

% Custom commands -------------------------------------------------------------

\newcommand{\heading}[1]{
	\vspace{8pt}
	\textbf{\large #1}
}
\newcommand{\subheading}[2]{
	\begin{tabular*}{\textwidth-\leftmargin}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
	\end{tabular*} \\
}
\newcommand{\itemheading}[2]{
	\vspace{1pt}
	\begin{tabular*}{\textwidth-\leftmargin}{l@{\extracolsep{\fill}}r}
		\textit{#1} & \textit{#2} \\
	\end{tabular*} \\
	\vspace{-2pt}
}

% Resume ----------------------------------------------------------------------

\begin{document}

\textbf{\huge Thomas Matthew Reay}

\vspace{4pt}

\begin{tabular*}{\textwidth}{l|l|l|l}
	\hline
	Tokyo, JP & 080-5000-2399 & tmattreay@gmail.com & thomasreay.info
	\rule{0pt}{12pt} \\
\end{tabular*}

\vspace{12pt}

Innovative and results-oriented professional offering four years of experience in physics, software/backend
development, frontend/desktop application development, consulting, data analysis, and client success,
additionally leveraging internships and a Bachelor of Science - please confirm, with a concentration in
Computational Physics to realize exemplary results and desired outcomes.

\line(1, 0){\textwidth}

\vspace{8pt}

\heading{Work Experience}

\begin{itemize}
\item
	\subheading{Enthought, Inc.}{Austin, TX | Tokyo, JP}
	\itemheading{Scientific Software Developer}{March 2018 - Aug. 2020}
	\vspace{2pt}
	\itemheading{Senior Scientific Software Developer}{Aug. 2020 - Present}
	\begin{itemize}
	    \item Developing applications and technical solutions for clients in the semi-conductor industry.
	    \item Working with clients to explore problem domains, plan project timelines, and establish user-friendly workflows.
		\item Designing web applications for text and image search with 1,000's of users, using React, Flask, Elasticsearch, and Keras.
		\item Designing processing pipelines for content extraction in Office and PDF documents, using Java and Libreoffice.
	    \item Managing the deployment of multiple distributed applications, using Ansible, Docker, and NGINX.
		\item Maintaining a code base of ~130K LOC for 4+ years, and teaching that code base to the client's development team for future maintenence.
	    \item Designed an image processing desktop application with 100's of users, using Python, Keras, Qt, etc.
		\item Served as project manager and techincal lead on multiple projects, resulting in a \$30 million USD contract extension for the next 5 years.
	\end{itemize}
	\itemheading{Tokyo Office Manager}{June 2020 - Present}
	\begin{itemize}
	    \item Developing applications and technical solutions for clients in the semi-conductor industry.
	    \item Working with clients to explore problem domains, plan project timelines, and establish user-friendly workflows.
	\end{itemize}

\item
	\subheading{Applied Research Laboratories: Space and Geophysics Lab}{Austin, TX}
	\itemheading{Research Engineering / Scientist Associate}{Sept. 2015 - March 2018}
	\begin{itemize}
	    \item Built software suite in Python for beam-forming / array signal processing.
		\item Produced visualizations of various geo-spacial data for academic conferences and publications.
    	\item Assisted in setup and operation of field experiments and data collection in challenging environments.
		\item Point of contact for testing and verification of software from partner labs.
	\end{itemize}
	\itemheading{Student Technician}{Nov. 2014 - May 2015}
	\begin{itemize}
    	\item Analyzing ionospheric data from GNSS network.
		\item Computational analysis with scientific Python suite.
	\end{itemize}

\item
	\subheading{University of Texas: Raizen Group}{Austin, TX}
	\itemheading{Research Engineering / Scientist Associate}{June 2015 - Aug. 2015}
	\begin{itemize}
    	\item Researched potential applications for graphene oxide structures.
	\end{itemize}
	\itemheading{Research Assistant}{June 2014 - Oct. 2014}
	\begin{itemize}
    	\item Designed an atomic hydrogen source for use in an ultra high-vacuum environment.
		\item Drafted and manufatured parts using CAD software and a mill / lathe.
    	\item Trained and mentored fellow undergraduate research assistants.
	\end{itemize}

\item
	\subheading{University of Texas: Liberal Arts ITS}{Austin, TX}
	\itemheading{Desktop Support Assistant}{June 2012 - Aug. 2014}
	\begin{itemize}
		\item Diagnosed and resolved miscellaneous IT issues for faculty and staff.
		\item Managed the processing and distribution of new computers for faculty.
	\end{itemize}
\end{itemize}

\heading{Education}

\begin{itemize}
	\item
		\subheading{University of Texas}{Austin, TX}
		\itemheading{BS, Computational Physics (GPA: 3.88; Hours: 137)}{Graduated with Honors, Spring 2015}
\end{itemize}

\heading{Core Competencies}

\begin{itemize}
	\item[] Cross-Functional Collaboration, Issue Resolution, Design, Application Development, Process Enhancements,
	Application Deployment, Requirement Translation, Optimization Techniques, Workflow Orchestration,
	Troubleshooting
\end{itemize}

\heading{Technical Skills}

\begin{itemize}
	\item
		\subheading{Programing Languages:}{}
		\itemheading{Python, Javascript, Java, SQL, Fortran, C, \LaTeX, Mathematica, MatLab}{}
	\item
		\subheading{Tools and Frameworks:}{}
		\itemheading{React, Flask, Docker, Ansible, PostgreSQL, Elasticsearch, Libreoffice, Keras}{}
\end{itemize}

\end{document}
